\section{The Game}

\todo{DO beter add some text here}
\subsection{Goal of The Game}
The objective of the game is for the player to achieve the highest possible score (measured as the vertical and horizontal distance)
by surviving for the longest possible duration while climbing the terrain.

\todo{Fix this}
\todo{Make hiker gender neutral}
\subsection{Entities}
\textbf{Hiker}
The hiker is controlled by the user of the game and his health is indicated by a health bar.
If the hiker loses all his health points or falls behind the kill bar, the hiker dies and the game ends.
The hiker has different movement options, including moving to the left and right in the x-direction, jumping and crouching.

\textbf{Kill Bar/Monster}
In the current version of the game, the kill bar is represented by a Yeti figure.
It is situated at the left edge of the screen and moves continuously while trying to catch the hiker.

\textbf{Items and Inventory}
There are items spawning during the course of the game which can be collected by the hiker:

\begin{itemize}
\item Kaiserschmarrn: Eating the delicious Kaiserschmarrn will restore the hiker's health.
\item Coin: Collecting a coin increases the coin score and increases the speed of the hiker.
\item Duck: The duck provides a shield for a few seconds. As long as the hiker has the shield, he won't take damage from being hit by rocks.
\item \todo{add bomb}
\end{itemize}

The items collected by the hiker are stored in an inventory.
The hiker can switch between the items in the inventory and select them for use.

\textbf{Rocks}
New rocks are continuously generated and propelled through the air.
When the hiker is hit by a rock, the hiker's health decreases.